---
title: "Exploratory analysis"
output: github_document
---

```{r setup}
library(tidyverse)
library(rvest)
```


## Setting options

```{r, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90"
)

theme_set(theme_minimal() + theme(legend.position = "botton"))

options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete = scale_color_viridis_d
```

## Do something simple

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)  

(x_vec - mean(x_vec))/sd(x_vec)

```

I want a function to compute z-scores

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}

z_scores(x_vec)
```

Try my function on some other things. These should give errors.

```{r, error = TRUE}
z_scores(3)
z_scores("my name is jeff")
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
```

## Multiple outputs
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3) {
    stop("Input must have at least three numbers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}

mean_and_sd(x_vec)
```

Check that the function works.

```{r}
mean_and_sd(x_vec)
```

## Multiple inputs

I'd like to do this with function
```{r}
sim_data = 
  tibble(
    x = rnorm(100, mean = 4, sd = 3)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
```

```{r}
sim_mean_sd = function(samp_size, mu = 0, sigma = 1){
  
  sim_data = 
    tibble(
      x = rnorm(n = samp_size, mean = mu, sd = sigma)
  )

sim_data %>% 
  summarize(
    mean = mean(x),
    sd = sd(x)
    )

}

sim_mean_sd(samp_size = 100, mu = 6, sigma = 3)
sim_mean_sd(mu = 6, samp_size = 100, sigma = 3)
sim_mean_sd(samp_size = 100)
```

## Let's review Napoleon Dynamite



```{r, eval = FALSE}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

What about the next page of reviews...

Let's turn that code into a function

```{r}
read_page_reviews = function(url){
  
  dynamite_html = read_html(url)

  review_titles = 
    dynamite_html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()

  review_stars = 
    dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()

  review_text = 
    dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()

  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
    )
  
    reviews
}
```

Let's try the function

```{r}
dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"

read_page_reviews(dynamite_url)
```

Let's read a few pages of reviews. 

```{r}
dynamite_url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

dynamite_urls = str_c(dynamite_url_base, 1:5)

all_reviews = 
  bind_rows(
    read_page_reviews(dynamite_urls[1]),
    read_page_reviews(dynamite_urls[2]),
    read_page_reviews(dynamite_urls[3]),
    read_page_reviews(dynamite_urls[4]),
    read_page_reviews(dynamite_urls[5])
  )

```

## Mean scoping example

```{r}
f = function(x) {
  z = x + y
  z
}
x = 1
y = 2
f(x = y)
```

## Functions as arguments

```{r}
my_summary = function(x, summ_func) {
  
  summ_func(x)
  
}
x_vec = rnorm(100, 3, 7)
mean(x_vec)
median(x_vec)
my_summary(x_vec, IQR)
```







